Appendix A - Alternative DSDM formulations

### 2019-10-22 manuscript/appendix_a.Rmd
tidy up and add reference

- `size`: a (positive) scalar giving the dispersion parameter of the negative binomial distribution
- `Lambda`: a (positive) vector of the relative abundances for each observation
- `y`: a vector of (non-negative) integers encoding count observations

```{r negbin_obs}
prob <- size / (size + Lambda)
distribution(y) <- negative_binomial(size, prob)
```

@@

Similarly to the biotic interactions model, we can consider a population of single species but with $L$ different genotypes with a blocked transition matrix. In this model, the genotypes are linked via reproduction rather than density-dependent vital rates. The $L$x$L$ matrix $\mathbf{m}$ quantifies mutation rates between different genotypes. For an individual of genotype $l$, each of its offspring has probability $\mathbf{m}_{l,l'}$ of being of genotype $l'$. Each genotype has its own vital rate sub-models, representing a linked phenotype driving population dynamics for that genotype. By analysing the combined transition matrix $\mathbf{A}^*_i$ at each site $i$ with different environmental covariates, the model can consider how selection for each genotype varies across the environment, and predict the genetic makeup of populations.

>>>>

- `r`: a (positive) scalar giving the dispersion parameter of the negative binomial distribution (equivalent to the `size` argument of `stats::dnbinom()`)
- `Lambda`: a (positive) vector of the relative abundances for each observation
- `y`: a vector of (non-negative) integers encoding count observations

```{r negbin_obs}
p <- r / (r + Lambda)
distribution(y) <- negative_binomial(r, p)
```

@@

Similarly to the biotic interactions model, we can consider a population of single species but with $L$ different genotypes with a blocked transition matrix. In this model, the genotypes are linked via reproduction rather than density-dependent vital rates. The $L$x$L$ matrix $\mathbf{m}$ quantifies mutation rates between different genotypes. For an individual of genotype $l$, each of its offspring has probability $\mathbf{m}_{l,l'}$ of being of genotype $l'$. Each genotype has its own vital rate sub-models, representing a linked phenotype driving population dynamics for that genotype. By analysing the combined transition matrix $\mathbf{A}^*_i$ at each site $i$ with different environmental covariates, the model can consider how selection for each genotype varies across the environment, and predict the genetic makeup of populations. Note that this is just one approach to considering multiple genotypes and natural selection in a matrix population model, see e.g. [@devriesSelectionTwosexStagestructured2019].
